Supplements for the manuscript ``Measuring individual differences in the understanding of gaze cues across the lifespan''

### 2022-09-02 supplements/supplements.Rmd
incorporate Daniel's feedback; pre-registration deviations; participant exclusions

---
title             : |
                    <center> Supplements for the manuscript </center>
                    <center> "Measuring individual differences in the understanding of gaze cues across the lifespan" </center>
shorttitle        : "Supplements"
author:

@@

  - name          : "Daniel M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

---
title             : |
                    <center> Supplements for the manuscript </center>
                    <center> "TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults" </center>
shorttitle        : "Supplements"
author:

@@

  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---
